Revisiting the Classics: Online RL in the Programmable Dataplane

### 2022-11-18 ngni-talk/arista-talk.tex
Forgot to upload some talk (sub-)variants

\usepackage{etoolbox}
\usepackage[binary-units]{siunitx}
\robustify\bfseries
\sisetup{detect-all, range-phrase=--, range-units=single}

@@

\title{Revisiting the Classics: Online RL in the Programmable Dataplane}
\author{\vspace{-1em}\textbf{Kyle A. Simpson}, Dimitrios P. Pezaros\\
	\faEnvelopeO{} \href{mailto:k.simpson.1@research.gla.ac.uk}{\nolinkurl{k.simpson.1@research.gla.ac.uk}}\\
	\vspace{1em}\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}}
\institute{University of Glasgow}
\date{\nth{4} June, 2021}

@@

\begin{frame}{Recent Programmable Trends in Data-Driven Networks}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{itemize}
				\item ML acceleration, line-rate packet classification.
				\item How? Train model off-NIC, convert to \alert{binary neural network}\footnotemark, or \alert{decision tree}\footnotemark.
				\item Limits? No online training, cost of backprop algo (expensive!), vast data needs.
				\item \alert{What if we need online learning?}
			\end{itemize}
		\end{column}
		\begin{column}{0.4\linewidth}
			\centering
			\resizebox{0.6\linewidth}{!}{
				\includegraphics{images/smartnic.png}
			}

			\resizebox{0.5\linewidth}{!}{
				\includegraphics{images/nn}
			}
		\end{column}
	\end{columns}
\setcounter{footnote}{1}
\footcitetext{DBLP:journals/corr/abs-2009-02353}
\setcounter{footnote}{2}
\footcitetext{DBLP:conf/hotnets/XiongZ19}
\end{frame}

@@

			\begin{itemize}
				\item PCIe access times $\mathcal{O}(\si{\micro\second})$\footnotemark
				\item Crossing VMs/vNFS has $\sim$\SI{10}{$\times$} higher cost\footnotemark
				\item MATs recompiled $\mathcal{O}(\si{\second})$. Many rules $\implies$ batching.
%				\item Thrift serde time $\mathcal{O}(\si{\milli\second})$.
			\end{itemize}

@@

			\alert{Meanwhile core-to-core on NFP around \SI{140}{\nano\second} @ \SI{1.2}{\giga\hertz}.}
		\end{column}
		\begin{column}{0.5\linewidth}
			\begin{figure}
				\includegraphics[width=0.9\linewidth]{../plots/build/rte-timer/rte-times-logx}
				\caption{Netronome rule installation cost \\(1 table, \numrange{1}{65536} rules).}
			\end{figure}
		\end{column}
	\end{columns}
	\setcounter{footnote}{3}
	\footcitetext{DBLP:conf/sigcomm/NeugebauerAZAL018}
	\setcounter{footnote}{4}
	\footcitetext{DBLP:journals/cm/CzivaP17}
\end{frame}

@@

@@

	\textbf{One NFP island $\implies$ \alert{\SI{15}{$\times$} median S$\rightarrow$A speedup}.}\pause

@@

>>>>

\usepackage{etoolbox}
\usepackage[binary-units]{siunitx}
\robustify\bfseries
\sisetup{detect-all, range-phrase=--, range-units=single, per-mode=symbol}

@@

\title{Revisiting the Classics: Online RL in the Programmable Dataplane \emph{(IEEE NOMS '22)}}
\author{\vspace{-1em}\textbf{Kyle A. Simpson}, Dimitrios P. Pezaros\\
	\faEnvelopeO{} \href{mailto:k.simpson.1@research.gla.ac.uk}{\nolinkurl{k.simpson.1@research.gla.ac.uk}}\\
	\vspace{1em}\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}}
\institute{University of Glasgow}
\date{\nth{27} October, 2022}

@@

\begin{frame}{Recent Programmable Trends in Data-Driven Networks}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{itemize}
				\item ML acceleration, line-rate packet classification.
				\item How? Train model off-NIC, convert to \alert{binary neural network}\footnotemark, or \alert{decision tree}\footnotemark.
				\item Bespoke architectures like \emph{Taurus}\footnotemark.
				\item Limits? No online training, cost of backprop algo (expensive!), vast data needs.
				\item \alert{What if we need online learning?}
			\end{itemize}
		\end{column}
		\begin{column}{0.4\linewidth}
			\centering
			\resizebox{0.6\linewidth}{!}{
				\includegraphics{images/smartnic.png}
			}

			\resizebox{0.5\linewidth}{!}{
				\includegraphics{images/nn}
			}
		\end{column}
	\end{columns}
\setcounter{footnote}{1}
\footcitetext{DBLP:journals/corr/abs-2009-02353}
\setcounter{footnote}{2}
\footcitetext{DBLP:conf/hotnets/XiongZ19}
\setcounter{footnote}{3}
\footcitetext{DBLP:journals/corr/abs-2002-08987}
\end{frame}

@@

			\begin{itemize}
				\item PCIe access times $\mathcal{O}(\si{\micro\second})$\footnotemark
				\item Crossing VMs/vNFS has $\sim$\qty{10}{\times} higher cost\footnotemark
				\item MATs recompiled $\mathcal{O}(\si{\second})$. Many rules $\implies$ batching.
%				\item Thrift serde time $\mathcal{O}(\si{\milli\second})$.
			\end{itemize}

@@

			\alert{Meanwhile core-to-core on NFP around \SI{140}{\nano\second} @ \SI{1.2}{\giga\hertz}.}
		\end{column}
		\begin{column}{0.5\linewidth}
			\begin{figure}
				\includegraphics[width=0.9\linewidth]{../plots/build/rte-timer/rte-times-logx}
				\caption{Netronome rule installation cost \\(1 table, \numrange{1}{65536} rules).}
			\end{figure}
		\end{column}
	\end{columns}
	\setcounter{footnote}{4}
	\footcitetext{DBLP:conf/sigcomm/NeugebauerAZAL018}
	\setcounter{footnote}{5}
	\footcitetext{DBLP:journals/cm/CzivaP17}
\end{frame}

@@

\begin{frame}{A primer on the Netronome NFP}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{itemize}
				\item PCIe NIC @ \qtyrange{40}{100}{\giga\bit\per\second}.
				\item \alert{NPU-type device}---many weak cores.
				\item One program per core, cooperative scheduling between HW threads.
				\item \textbf{Programming Model:}
				\begin{itemize}
					\item (P4) -> $\mu$C -> Proprietary ASM.
					\item Explicit locality of compute \& memory.
				\end{itemize}
			\end{itemize}
		\end{column}
		\begin{column}{0.4\linewidth}
			\centering
			\resizebox{0.8\linewidth}{!}{
				\includegraphics{images/smartnic.png}
			}
		\end{column}
	\end{columns}
\end{frame}

@@

	\textbf{One NFP island $\implies$ \alert{\qty{15}{\times} median S$\rightarrow$A speedup}.}\pause

@@

\begin{frame}{Feasibility on other architectures?}
	\begin{itemize}[<+->]
		\item \textbf{Tofino etc.?} \alert{Unlikely}.
		\item \textbf{Taurus?\footcite{DBLP:journals/corr/abs-2002-08987}} Exec model \emph{almost} right, but \alert{read-only}.
		\item \textbf{FPGA?} Probably an effective match to this model + algorithm.
		\item Research gap: hardware architectures built to collate and apply batches of samples, gradient updates?
	\end{itemize}
\end{frame}

### 2022-11-18 ngni-talk/noms-talk.tex
Forgot to upload some talk (sub-)variants

\usepackage{etoolbox}
\usepackage[binary-units]{siunitx}
\robustify\bfseries
\sisetup{detect-all, range-phrase=--, range-units=single, per-mode=symbol}

@@

\title{Revisiting the Classics: Online RL in the Programmable Dataplane \emph{(IEEE NOMS '22)}}
\author{\vspace{-1em}\textbf{Kyle A. Simpson}, Dimitrios P. Pezaros\\
	\faEnvelopeO{} \href{mailto:k.simpson.1@research.gla.ac.uk}{\nolinkurl{k.simpson.1@research.gla.ac.uk}}\\
	\vspace{1em}\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}}
\institute{University of Glasgow}
\date{\nth{27} October, 2022}

@@

\begin{frame}{Recent Programmable Trends in Data-Driven Networks}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{itemize}
				\item ML acceleration, line-rate packet classification.
				\item How? Train model off-NIC, convert to \alert{binary neural network}\footnotemark, or \alert{decision tree}\footnotemark.
				\item Bespoke architectures like \emph{Taurus}\footnotemark.
				\item Limits? No online training, cost of backprop algo (expensive!), vast data needs.
				\item \alert{What if we need online learning?}
			\end{itemize}
		\end{column}
		\begin{column}{0.4\linewidth}
			\centering
			\resizebox{0.6\linewidth}{!}{
				\includegraphics{images/smartnic.png}
			}

			\resizebox{0.5\linewidth}{!}{
				\includegraphics{images/nn}
			}
		\end{column}
	\end{columns}
\setcounter{footnote}{1}
\footcitetext{DBLP:journals/corr/abs-2009-02353}
\setcounter{footnote}{2}
\footcitetext{DBLP:conf/hotnets/XiongZ19}
\setcounter{footnote}{3}
\footcitetext{DBLP:journals/corr/abs-2002-08987}
\end{frame}

@@

			\alert{Meanwhile core-to-core on NFP around \SI{140}{\nano\second} @ \SI{1.2}{\giga\hertz}.}
		\end{column}
		\begin{column}{0.5\linewidth}
			\begin{figure}
				\includegraphics[width=0.9\linewidth]{../plots/build/rte-timer/rte-times-logx}
				\caption{Netronome rule installation cost \\(1 table, \numrange{1}{65536} rules).}
			\end{figure}
		\end{column}
	\end{columns}
	\setcounter{footnote}{4}
	\footcitetext{DBLP:conf/sigcomm/NeugebauerAZAL018}
	\setcounter{footnote}{5}
	\footcitetext{DBLP:journals/cm/CzivaP17}
\end{frame}

@@

\begin{frame}{A primer on the Netronome NFP}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{itemize}
				\item PCIe NIC @ \qtyrange{40}{100}{\giga\bit\per\second}.
				\item \alert{NPU-type device}---many weak cores.
				\item One program per core, cooperative scheduling between HW threads.
				\item \textbf{Programming Model:}
				\begin{itemize}
					\item (P4) -> $\mu$C -> Proprietary ASM.
					\item Explicit locality of compute \& memory.
				\end{itemize}
			\end{itemize}
		\end{column}
		\begin{column}{0.4\linewidth}
			\centering
			\resizebox{0.8\linewidth}{!}{
				\includegraphics{images/smartnic.png}
			}
		\end{column}
	\end{columns}
\end{frame}

@@

\begin{frame}{Feasibility on other architectures?}
	\begin{itemize}[<+->]
		\item \textbf{Tofino etc.?} \alert{Unlikely}.
		\item \textbf{Taurus?\footcite{DBLP:journals/corr/abs-2002-08987}} Exec model \emph{almost} right, but \alert{read-only}.
		\item \textbf{FPGA?} Probably an effective match to this model + algorithm.
		\item Research gap: hardware architectures built to collate and apply batches of samples, gradient updates?
	\end{itemize}
\end{frame}

>>>>

\usepackage{etoolbox}
\usepackage[binary-units]{siunitx}
\robustify\bfseries
\sisetup{detect-all, range-phrase=--, range-units=single}

@@

\title{Revisiting the Classics: Online RL in the Programmable Dataplane}
\author{\vspace{-1em}\textbf{Kyle A. Simpson}, Dimitrios P. Pezaros\\
	\faEnvelopeO{} \href{mailto:k.simpson.1@research.gla.ac.uk}{\nolinkurl{k.simpson.1@research.gla.ac.uk}}\\
	\vspace{1em}\small{\faGithub{} \href{https://github.com/felixmcfelix}{FelixMcFelix} \hspace{0.5em} \faGlobe{} \url{https://mcfelix.me}}}
\institute{University of Glasgow}
\date{\nth{26} April, 2022}

@@

\begin{frame}{Recent Programmable Trends in Data-Driven Networks}
	\begin{columns}
		\begin{column}{0.6\linewidth}
			\begin{itemize}
				\item ML acceleration, line-rate packet classification.
				\item How? Train model off-NIC, convert to \alert{binary neural network}\footnotemark, or \alert{decision tree}\footnotemark.
				\item Limits? No online training, cost of backprop algo (expensive!), vast data needs.
				\item \alert{What if we need online learning?}
			\end{itemize}
		\end{column}
		\begin{column}{0.4\linewidth}
			\centering
			\resizebox{0.6\linewidth}{!}{
				\includegraphics{images/smartnic.png}
			}

			\resizebox{0.5\linewidth}{!}{
				\includegraphics{images/nn}
			}
		\end{column}
	\end{columns}
\setcounter{footnote}{1}
\footcitetext{DBLP:journals/corr/abs-2009-02353}
\setcounter{footnote}{2}
\footcitetext{DBLP:conf/hotnets/XiongZ19}
\end{frame}

@@

			\alert{Meanwhile core-to-core on NFP around \SI{140}{\nano\second} @ \SI{1.2}{\giga\hertz}.}
		\end{column}
		\begin{column}{0.5\linewidth}
			\begin{figure}
				\includegraphics[width=0.9\linewidth]{../plots/build/rte-timer/rte-times-logx}
				\caption{Netronome rule installation cost \\(1 table, \numrange{1}{65536} rules).}
			\end{figure}
		\end{column}
	\end{columns}
	\setcounter{footnote}{3}
	\footcitetext{DBLP:conf/sigcomm/NeugebauerAZAL018}
	\setcounter{footnote}{4}
	\footcitetext{DBLP:journals/cm/CzivaP17}
\end{frame}

@@

@@
